Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-05-22 Chapter-2/2-LArTPCs.tex
s

\chapter{Liquid Argon Detectors at the Intensity Frontier}\label{ch:2}
%{\raggedleft ``\emph{Beat-up little seagull, on a marble stair} \par}
%{\raggedleft \emph{Tryin' to find the ocean, lookin' everywhere.}"\par}
%{\raggedleft -- Nina Simone, Baltimore, 1978 -- \par}
%\vspace{0.5cm}

>>>>

\chapter{Liquid Argon Detectors at the Intensity Frontier}\label{ch:2}
{\raggedleft ``\emph{Beat-up little seagull, on a marble stair} \par}
{\raggedleft \emph{Tryin' to find the ocean, lookin' everywhere.}"\par}
{\raggedleft -- Nina Simone, Baltimore, 1978 -- \par}
\vspace{0.5cm}

### 2018-05-22 Chapter-3/3-TheLArIATExperiment.tex
s

\chapter{LArIAT: Liquid Argon In A Testbeam}\label{sec:experimentDescription}
In this chapter, we describe the LArIAT experimental setup. We start by illustrating the journey of the charged particles in the Fermilab accelerator complex, from the gaseous thermal hydrogen at the Fermilab ion source to the delivery of the LArIAT tertiary beam at MC7. We  then describe the LArIAT beamline detectors, the LArTPC, the DAQ and the monitoring system.

>>>>

\chapter{LArIAT: Liquid Argon In A Testbeam}\label{sec:experimentDescription}
{\raggedleft ``\emph{But hey we need to be somewhat foolish,} \par}
{\raggedleft \emph{feebleminded, wrong and senseless.}"\par}
{\raggedleft -- Agnes Obel, Avenue, 2010 -- \par}
\vspace{0.5cm}

In this chapter, we describe the LArIAT experimental setup. We start by illustrating the journey of the charged particles in the Fermilab accelerator complex, from the gaseous thermal hydrogen at the Fermilab ion source to the delivery of the LArIAT tertiary beam at MC7. We  then describe the LArIAT beamline detectors, the LArTPC, the DAQ and the monitoring system.

### 2018-05-22 Chapter-4/4-Methodology.tex
s

\chapter{Total Hadronic Cross Section Measurement Methodology}\label{ch:Interactions}
%{\raggedleft ``\emph{Like a lemon to the lime and the bubble to the bee}" \par}
%{\raggedleft -- Eazy-E, Gimmie that Nutt,  1993 -- \par}
%\vspace{0.5cm}

>>>>

\chapter{Total Hadronic Cross Section Measurement Methodology}\label{ch:Interactions}
{\raggedleft ``\emph{Like a lemon to the lime and the bubble to the bee}" \par}
{\raggedleft -- Eazy-E, Gimmie that Nutt,  1993 -- \par}
\vspace{0.5cm}

### 2018-05-22 Chapter-5/5-Preparatory.tex
s

\chapter{Data and MC preparation for the Cross Section Measurements}\label{ch:samples}
%{\raggedleft ``\emph{Il dolce non lo mangi mai, ma qualche volta ti rifai.} \par}
%{\raggedleft \emph{Abbracciami}"\par}
%{\raggedleft -- Pietro Ciampi, L'amore e' tutto qui, 1971 -- \par}
%\vspace{0.5cm}

%{\raggedleft ``\emph{You never eat dessert, but, sometimes, you make up for it.} \par}
%{\raggedleft \emph{Hug me}"\par}
%{\raggedleft -- Pietro Ciampi, L'amore e' tutto qui, 1971 -- \par}
%\vspace{0.5cm}

>>>>

\chapter{Data and MC preparation for the Cross Section Measurements}\label{ch:samples}
{\raggedleft ``\emph{Il dolce non lo mangi mai, ma qualche volta ti rifai.} \par}
{\raggedleft \emph{Abbracciami}"\par}
{\raggedleft -- Pietro Ciampi, L'amore e' tutto qui, 1971 -- \par}
\vspace{0.5cm}

### 2018-05-22 Chapter-6/6-PionCrossSection.tex
s

\chapter{Negative Pion Cross Section Measurement}\label{ch:PionXS}
%{\raggedleft ``\emph{Y ella es flama que se eleva, Y es un p\'ajaro a volar.} \par}
%{\raggedleft \emph{En la noche que se incendia, estrella de oscuridad}\par}
%{\raggedleft \emph{que busca entre la tiniebla, la dulce hoguera del beso.}"\par}
%{\raggedleft -- Lila Downs, Benediction And Dream,  2002 -- \par}
%\vspace{0.5cm}

>>>>

\chapter{Negative Pion Cross Section Measurement}\label{ch:PionXS}
{\raggedleft ``\emph{Y ella es flama que se eleva, Y es un p\'ajaro a volar.} \par}
{\raggedleft \emph{En la noche que se incendia, estrella de oscuridad}\par}
{\raggedleft \emph{que busca entre la tiniebla, la dulce hoguera del beso.}"\par}
{\raggedleft -- Lila Downs, Benediction And Dream,  2002 -- \par}
\vspace{0.5cm}
